
%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\RequirePackage{fontawesome}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% -------- Margins (tightened only) --------
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{1.45in}

\urlstyle{rm}
\raggedright
\setlength{\tabcolsep}{0in}

% -------- Global spacing compression --------
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\setlength{\itemsep}{1pt}
\setlength{\topsep}{1pt}

% -------- Section formatting --------
\titleformat{\section}{
  \vspace{-12pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule \vspace{-8pt}]

% -------- Commands --------
\newcommand{\resumeItem}[2]{
  \item\small{\textbf{#1}: #2}
}

\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{
  \begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\topsep}{1pt}
}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-----------------------------
\begin{document}

%----------HEADING----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Tridhatri Sontena}} & \\

  \faEnvelope\ \href{mailto:tridhatri.sontena@gmail.com}{tridhatri.sontena@gmail.com} &
  \faGithub\ \href{https://github.com/Tridhatri}{github.com/Tridhatri} \\

  \faEnvelope\ \href{mailto:tridhatri.sontena@intel.com}{tridhatri.sontena@intel.com} &
  \faLinkedin\ \href{https://www.linkedin.com/in/tridhatri-sontena-484934224}{linkedin.com/in/tridhatri-sontena} \\

  \faPhone\ +91-7337337537 &
  \faGlobe\ \href{https://tridhatri.vercel.app}{tridhatri.vercel.app} \\
\end{tabular*}


%-----------SKILLS-----------
\section{Skills Summary}
\resumeSubHeadingListStart
\resumeItem{Programming Languages}{Python, C/C++, Lua, SQL, Vim Script, Java, JavaScript, Bash, PowerShell, typst}
\resumeItem{Systems \& Debugging}{Windows Performance Analyzer (WPA), GPUView, WinDbg, WPT, GPU Debugging, Graphics IP, Display Debugging, ETL Analysis, Performance Analysis, Log Analysis}
\resumeItem{Tools}{Git, GitHub, NeoVim, Vim, tmux, kitty, LaTeX}
\resumeItem{Platforms}{Linux (Arch, Ubuntu, Debian), Unix, Windows, macOS}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading{Intel Corporation}{On-site}
{GPU SDE Debugger Intern}{July 2025 -- Present}
\resumeItemListStart

\resumeItem{Agentic AI Debug App}
{Architected and built an end-to-end Agentic AI command-line application to automate GPU driver defect analysis, reducing manual triage time from 10--20 minutes to an average of 2.7 minutes (87\% improvement). Interfaced with internal defect-tracking REST APIs to pull live issue metadata, attachments, and engineer comments as structured LLM context.

\vspace{2pt}
Designed a 6-phase multi-agent pipeline: (1) automated data ingestion and log classification (ETL, GOP, crash-dump, burnin, performance traces), (2) interactive attachment selection with a user-driven per-item analysis loop, (3) LLM-orchestrated per-category analysis using specialized agent tools and skills, (4) RAG-powered triage checklist compliance and best-known methodology retrieval from internal knowledge bases, (5) structured JSON report generation via a dedicated agent tool, and (6) rendered HTML report artifact with a plaintext terminal summary. Built 19 tool integrations and agent skills spanning 20 defect categories (Display, Media, BSOD, TDR, Gaming, AI/ML, etc.). Orchestrated two external AI analysis pipelines via subprocess with dynamic prompt construction derived from defect context. Applied multithreading, content-hash caching, and context-window compression to minimize LLM token overhead. Built a custom QA evaluation framework for continuous accuracy measurement.\\
\textbf{Stack: Python, Enterprise LLMs, Agentic AI, RAG, LLM Tool-Use, Multi-Agent Systems, ETL, WPA, WinDbg, GPUView, WPT, Roff, HTML/CSS, JSON, REST APIs}
}

\resumeItem{Graphics Driver Debug Core Work}
{Debugging low-level Graphics IP issues with a focus on display technologies and OS-Graphics Driver-External Device interactions. Involved in identifying, analyzing, and resolving Graphics Driver and GOP driver faults to improve stability and correctness.}

\resumeItemListEnd

\resumeSubheading{C.R. Rao Advanced Institute of Mathematics, Statistics and Computer Science}{On-site}
{Research Intern (Part-time)}{May 2024 -- August 2024}
\resumeItemListStart
\resumeItem{Limited Dataset Analysis}
{Conducted research on cybersecurity datasets under limited-data constraints, focusing on anomaly detection and improving data quality and balance using synthetic data generation and limited dataset analysis techniques to enable effective machine learning.}
\resumeItemListEnd

\resumeSubheading{Kellton Tech}{On-site}
{Student Developer (Part-time)}{May 2023 -- July 2023}
\resumeItemListStart
\resumeItem{Domain-Specific Chatbot}
{Built a custom domain-specific chatbot using OpenAI APIs with Python and Jupyter Notebooks; performed internal payroll data analysis and generated automated summaries and insights.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Hyderabad}{Hyderabad, India}
{Integrated Master of Technology (I.M.Tech) -- Computer Science}{Nov 2021 -- May 2026 (Expected)}
\resumeItemListStart
\resumeItem{Relevant Coursework}{Operating Systems, Unix Network Programming, Machine Learning, Neural Networks, Algorithms, Virtualization, DBMS, Computer Organisation and Architecture, Internet Technologies, Essentials of AI}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Academic Projects}
\resumeSubHeadingListStart

\resumeItem{Minimal Operating System -- 1000-Line Kernel}
{Built a bootable RISC-V kernel in C and Assembly featuring physical and virtual memory management, process scheduling, system calls, and paging. Implemented trap handling and context switching using OpenSBI, and validated kernel functionality using QEMU-based emulation. \\
\textbf{Link:} \href{https://github.com/Tridhatri/Kernel_Project}{github.com/Tridhatri/RISC\_V-OS}}

\resumeItem{Computer Vision Referee Assistant (HoopsEye)}
{Developed an automated basketball foul and ball detection system using YOLOv8 and OpenCV, integrated with a Flask backend for real-time inference and event visualization. Designed the pipeline for frame preprocessing, object detection, and inference optimization to assist referees during live gameplay. \\
\textbf{Link:} \href{https://github.com/Tridhatri/Automating-Basketball-Referee}{github.com/Tridhatri/Automating-Basketball-Referee}}

\resumeItem{Corotu -- Coroutine Runtime with Priority \& EDF Scheduling}
{Built a Go-inspired coroutine runtime in C addressing Go's lack of task prioritization. Implemented M:N cooperative scheduling with 8-level priority queues and EDF (Earliest Deadline First) scheduling -- provably optimal for meeting task deadlines. Features custom ARM64 assembly context switching (replacing broken \texttt{ucontext} on macOS), per-coroutine \texttt{mmap}'d stacks with guard-page overflow protection, and work-stealing across OS threads. Benchmarked against Go goroutines, libco, and libmill on context switch throughput and deadline miss rate. \\
\textbf{Stack: C, ARM64 Assembly, pthreads, mmap} \\
\textbf{Link:} \href{https://github.com/Tridhatri/corotu}{github.com/Tridhatri/corotu}}

\resumeItem{TCP Concurrent Student Database}
{Implemented a multi-client TCP concurrent server in C using processes and sockets to manage student and course records. Designed streamlined request/response protocols, ensured synchronization across clients, and handled concurrent read/write operations as part of Unix Network Programming coursework. \\
\textbf{Link:} \href{https://github.com/Tridhatri/TCP-Student-Database-in-C}{github.com/Tridhatri/TCP-Student-Database-in-C}}

\resumeSubHeadingListEnd

\end{document}
